Domestic cooking and likelihood

### 2020-01-27 inst/cook.Rmd
more detail

[as a consistency check we can perform the same calculation with a
slightly different value for `small`:

>>>>

See how the constraint is active: the strength of the training effect
is almost exactly equal to its maximal value of `small` [as a
consistency check we can perform the same calculation with a slightly
different value for `small`:
